New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2024-07-31 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
Sachen

>>>>

Next, we examined HR changes (i.e., mean slopes) within each interval to
test for the hypothesis that HR increased during the pre-teaching
interval and decreased during all other intervals (Hypothesis 1b). The
mean intercepts and mean slopes, complemented by their standard
deviations for each interval, are shown in Table 2; the graphical
representation of the slopes is displayed in Figure 5. The mean slope of
the pre-teaching interval (I1) was significantly positive, indicating an
increase in HR, as hypothesized. Further, the mean slopes of the
teaching interval (I2) and post-teaching interval (I3) were
significantly negative, indicating a decrease in HR. For the last two
intervals, the interview interval (I4) and end interval (I5), the mean
slope was negative but did not differ significantly from zero.

\input{tab_2.tex}

```
